---
title: "Assignment1"
author: "SIYU LIU(U74835706)"
date: "2/4/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(skimr)
library(lfe)
```

Randomization check by genders
```{r Question1.1}
f = read.csv('assignment/assignment1.csv')

f$gender2 <- ifelse(f$gender =='female',1, 0)

t <- f %>% filter(Treatment == 1)
c <- f %>% filter(Treatment == 0)
diff <- mean(t$gender2)-mean(c$gender2)
diffre <- diff/mean(c$gender2)*100

diffSE <- sqrt(sd(t$gender2)^2 / nrow(t) 
               + sd(c$gender2)^2 / nrow(c))

ciLow <- diff - 1.96*diffSE
ciHigh <- diff + 1.96*diffSE

paste('absolute difference:',diff)
paste('relative difference(%):',diffre)
paste('standard error:',diffSE)
paste('lower boundary:',ciLow)
paste('higher boundary:',ciHigh)
```

We can not reject diff  =  0 in 95% confidence interval, hence there is no significent difference of women proption between treatment group and control group. 

Randomization check by past sales
```{r Assignment 1.2}

diff_pass <- mean(t$past_sales)-mean(c$past_sales)
diffre_pass <- diff/mean(c$past_sales)*100

diffSE_pass <- sqrt(sd(t$past_sales)^2 / nrow(t) 
               + sd(c$past_sales)^2 / nrow(c))
ciLow_pass <- diff_pass - 1.96*diffSE_pass
ciHigh_pass <- diff_pass + 1.96*diffSE_pass

paste('diffrence:',diff_pass)
paste('relative difference(%):',diffre_pass)
paste('standard error:',diffSE_pass)
paste('lower boundary:',ciLow_pass)
paste('higher boundary:',ciHigh_pass)

```

Still, We can not reject diff  =  0 in 95% confidence interval, hence there is no significent difference of past sales between treatment group and control group.

```{r  Assignment 2}
##3. estimate effect without control. 

diff_itt <- mean(t$sales)-mean(c$sales)
diffre_itt <- diff_itt/mean(c$sales)*100

diffSE_itt <- sqrt(sd(t$sales)^2 / nrow(t) 
               + sd(c$sales)^2 / nrow(c))

ciLow_itt <- diff_itt - 1.96*diffSE_itt
ciHigh_itt <- diff_itt + 1.96*diffSE_itt

paste('diffrence:',diff_itt)
paste('relative difference(%):',diffre_itt)
paste('standard error:',diffSE_itt)
paste('lower boundary:',ciLow_itt)
paste('higher boundary:',ciHigh_itt)
```

Accoding to the regression summary, the effect is -0.001258 with standard error is  0.00927. We can not reject diff  =  0 in 95% confidence interval, hence there is we cannot say this campaign has an impact on sales.


```{r Question3.1}
complier <- f %>% filter(saw_ads == 1)

##randomization check on gender
t_complier <- complier %>% filter(Treatment == 1)
c_complier <- complier %>% filter(Treatment == 0)
diff_placebo <- mean(t_complier$gender2)-mean(c_complier$gender2)
diffre_placebo <- diff_placebo/mean(c_complier$sales)*100

diffSE_placebo <- sqrt(sd(t_complier$gender2)^2 / nrow(t_complier) 
               + sd(c_complier$gender2)^2 / nrow(c_complier))

ciLow_placebo <- diff_placebo - 1.96*diffSE_placebo
ciHigh_placebo <- diff_placebo + 1.96*diffSE_placebo

paste('diffrence:',diff_placebo)
paste('relative difference(%):',diffre_placebo)
paste('standard error:',diffSE_placebo)
paste('lower boundary:',ciLow_placebo)
paste('higher boundary:',ciHigh_placebo)

```


We can not reject diff  =  0 in 95% confidence interval, hence there is no significent difference of gender proption between treatment group and control group. 

```{r Question3.2}
diff_placebo2 <- mean(t_complier$past_sales)-mean(c_complier$past_sales)

diffre_placebo2 <- diff_placebo2/mean(c_complier$past_sales)*100
diffSE_placebo2 <- sqrt(sd(t_complier$past_sales)^2 / nrow(t_complier) 
               + sd(c_complier$past_sales)^2 / nrow(c_complier))

ciLow_placebo2 <- diff_placebo2 - 1.96*diffSE_placebo2
ciHigh_placebo2 <- diff_placebo2 + 1.96*diffSE_placebo2

paste('absolute diffrence:',diff_placebo2)
paste('relative difference(%):',diffre_placebo2)
paste('standard error:',diffSE_placebo2)
paste('lower boundary:',ciLow_placebo2)
paste('higher boundary:',ciHigh_placebo2)
```


We can not reject diff  =  0 in 95% confidence interval, hence there is no significent difference past sales between treatment group and control group. 

```{r Question4}
## accoding to the summary,
diff_tot <- mean(t_complier$sales)-mean(c_complier$sales)#0.040504

diffre_tot <- diff_tot/mean(c_complier$sales)*100
diffSE_tot <- sqrt(sd(t_complier$sales)^2 / nrow(t_complier) 
               + sd(c_complier$sales)^2 / nrow(c_complier))#0.011167

ciLow_tot <- diff_tot - 1.96*diffSE_tot
ciHigh_tot <- diff_tot + 1.96*diffSE_tot

paste('absolute diffrence:',diff_tot)
paste('relative difference(%):',diffre_tot)
paste('standard error:',diffSE_tot)
paste('lower boundary:',ciLow_tot)
paste('higher boundary:',ciHigh_tot)
```

The TOT standard error is more narrowed. We can reject 0 in 95% significant level and conclude that the effect is positive. 


```{r Question5.a}
total_diff_itt <- diff_itt* nrow(t)
total_diffre_itt <-diffre_itt

total_diffSE_itt <- diffSE_itt * nrow(t)

ciLow_totalitt <- total_diff_itt - 1.96*total_diffSE_itt
ciHigh_totalitt <- total_diff_itt + 1.96*total_diffSE_itt

paste('absolute diffrence:',total_diff_itt)
paste('relative difference(%):',total_diffre_itt)
paste('standard error:',total_diffSE_itt)
paste('lower boundary:',ciLow_totalitt)
paste('higher boundary:',ciHigh_totalitt)

```

```{r Question5b}
total_diff_tot <- diff_tot* nrow(t_complier)
total_diffre_tot <-diffre_tot

total_diffSE_tot <- diffSE_tot * nrow(t_complier)

ciLow_totaltot <- total_diff_tot - 1.96*total_diffSE_tot
ciHigh_totaltot <- total_diff_tot + 1.96*total_diffSE_tot

paste('absolute diffrence:',total_diff_tot)
paste('relative difference(%):',total_diffre_tot)
paste('standard error:',total_diffSE_tot)
paste('lower boundary:',ciLow_totaltot)
paste('higher boundary:',ciHigh_totaltot)
```

Question 5c
I will report the average Treatment on Treated because it will give a more accurate results on effects of advertisment. In this case, the standard error of TOT is more narrowed. It is less noisy and help us to get more concise effects.

Question 5d
This campaign is quite success based on the positive effect on sales. We got 0.01 incremental increase per exposed user and we have 95% confidence it number is significant difference from zero. However, we still need more information to measure the profit and make the further decision like the advertisement investment. 

```{r Question6}
obs = f %>% filter(Treatment == 1)
t_obs = obs %>% filter(saw_ads == 1)
c_obs = obs %>% filter(saw_ads == 0)

diff_obs <- mean(t_obs$sales)-mean(c_obs$sales)
diffre_obs <- diff_obs/mean(c_obs$sales)*100

diffSE_obs <- sqrt(sd(t_obs$sales)^2 / nrow(t_obs) 
               + sd(c_obs$sales)^2 / nrow(c_obs))

ciLow_obs <- diff_obs - 1.96*diffSE_obs
ciHigh_obs <- diff_obs + 1.96*diffSE_obs

paste('diffrence:',diff_obs)
paste('relative difference(%):',diffre_obs)
paste('standard error:',diffSE_obs)
paste('lower boundary:',ciLow_obs)
paste('higher boundary:',ciHigh_obs)
```

Question 6b
Without experiment, Manager may get toally wrong conclusions because of the selection bias. In this case, the observational study will conclude a negative effects of advertisement on sales while the experiment will get the opposite conclusion.

```{r Question7.a}

female = f %>% filter(gender2 == 1)

diff_fe <- mean(female$sales[female$Treatment == 1&female$saw_ads == 1])-
           mean(female$sales[female$Treatment == 0&female$saw_ads == 1])

diffre_fe <- diff_fe/mean(female$sales[female$Treatment == 0&female$saw_ads == 1])*100

diffSE_fe <- sqrt(sd(female$sales[female$Treatment == 1&female$saw_ads == 1])^2 /sum(female$Treatment == 1) + sd(female$sales[female$Treatment == 0&female$saw_ads == 1])^2 /sum(female$Treatment == 0))

ciLow_fe <- diff_fe - 1.96*diffSE_fe
ciHigh_fe <- diff_fe + 1.96*diffSE_fe

paste('diffrence:',diff_fe)
paste('relative difference(%):',diffre_fe)
paste('standard error:',diffSE_fe)
paste('lower boundary:',ciLow_fe)
paste('higher boundary:',ciHigh_fe)
```

```{r question 7b}
male = f %>% filter(gender2 == 0)

diff_ma <- mean(male$sales[male$Treatment == 1&male$saw_ads == 1])-
           mean(male$sales[male$Treatment == 0&male$saw_ads == 1])
diffre_ma <- diff_ma/mean(male$sales[male$Treatment == 0&male$saw_ads == 1])*100

diffSE_ma <- sqrt(sd(male$sales[male$Treatment == 1&male$saw_ads == 1])^2 / sum(male$Treatment == 1) 
               + sd(male$sales[male$Treatment == 0&male$saw_ads == 1])^2 / sum(male$Treatment == 0))

ciLow_ma <- diff_ma - 1.96*diffSE_ma
ciHigh_ma <- diff_ma + 1.96*diffSE_ma

paste('diffrence:',diff_ma)
paste('relative difference(%):',diffre_ma)
paste('standard error:',diffSE_ma)
paste('lower boundary:',ciLow_ma)
paste('higher boundary:',ciHigh_ma)
```

7c
Advertisement in female have more positive impact on sales compared to the male. In the female segmentation, the effect is 0.12 and significant difference from zero while in segemenation of male, we even can not conclude the effect is different from zero. Hence, if possible, we should target more female in our campaign.